---
title: "Lab9"
date: "2018/11/13"
output: pdf_document
---

# Q1
```{r}
set.seed(999)
library(microbenchmark)

odd_count<-function (x){
  odd_num = 0
  for (i in 1:length(x)){
    if (x[i] %% 2 ==1)
      odd_num <- odd_num +1
  }
  return(odd_num)
}

odd_count2 <- function(x){
  odd_num = 0
  odd_num <- sum(x %% 2 == 1)
  return(odd_num)
}

microbenchmark(odd_count(1:1000), odd_count2(1:1000))

```

We found that the Vectorized one is faster.

# Q2
```{r}

sort_vec<-function (x, ascending = TRUE){
  if(length(x) <2){
    return (x)
  }
  else{
    for (last in length(x):2){
      for (first in 1:(last -1)){
        if (x[first]> x[first+1]){
          temp <-x[first]
          x[first] = x[first +1]
          x[first +1] = temp
        }
      }
    }
  }
  if (ascending == FALSE){
    for (last in length(x):2){
      for (first in 1:(last-1)){
        if(x[first]<x[first +1]){
          temp<-x[first]
          x[first] = x[first +1]
          x[first +1] = temp
        }
      }
    }
  }
  return (x)
}

sort_vec(c(3, 1, 2), ascending = TRUE) 
sort_vec(c(3, 1, 2), ascending = FALSE) 

```


# Q3
## N=1000
```{r}
set.seed(999)
N = 1000
#dynamically allocated memory
data_series = 0 
system.time({
  for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})
#preallocated memory
system.time({
  data_series2 = vector(length = N)
  for (i in 2:N) {
    data_series2[i] = data_series2[i-1] + sample(c(-1, 1), 1)
  }
})
```
There is not obvious difference between dynamically allocated memory and preallocated memory

## N=10000
```{r}
set.seed(999)
N = 10000
#dynamically allocated memory
data_series = 0 
system.time({
  for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})

#preallocated memory
system.time({
  data_series2 = vector(length = N)
  for (i in 2:N) {
    data_series2[i] = data_series2[i-1] + sample(c(-1, 1), 1)
  }
})
```
When N = 10000, we find that the preallocated memory is faster than the dynamically allocated memory but there only a tiny difference.


## N=1000000
```{r}
set.seed(999)
N = 1000000
#dynamically allocated memory
data_series = 0 
system.time({
  for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
}
})

#preallocated memory
data_series2 = vector(length = N)
system.time({
  for (i in 2:N) {
    data_series2[i] = data_series2[i-1] + sample(c(-1, 1), 1)
  }
})

```
When N = 1000000, we find that there is obvious difference between dynamically allocated memory and preallocated memory that the second one is much faster than the first one.



